---
title: "Untitled"
author: "Jaynell Anderson"
date: "20 November 2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
sim = read.csv('Simdata.csv', header=TRUE)
attach(sim)
```

# Introduction
This data was taken from .. The data set contains observation from job applicants on their sim score are strength, grip and rating.

We write three models :
1. sims = f(arms)
2. sims = f(grip)
3. sims = f(arm,grip)

## first model

```{r}
model1 = lm(SIMS~ARM)
# scatterplot
plot(ARM, SIMS)
abline(model1)
```


This scatterplot shows that the SIMS = -4.09 + 0.5 * ARM. This equation is a straight line through the points on the scatterplot.

```{r}
# numeric summary
summary.lm(model1)
```
The numeric summary states the SIMS equation and shows that if and when put on a scatterplot it creates a straight line through the points on the plot.




The prediction interval from model1 when arm=94, grip=88 is : 
```{r}
newdata = data.frame(ARM=94, GRIP=88)
predict(model1, newdata, interval= 'prediction')
```

the predicted values is the first value (fit) and the next two values are the lower and upper prediction values.

## second model

```{r}
model2 = lm(SIMS~GRIP)
# scatterplot
plot(GRIP, SIMS)
abline(model2)
```


This scatterplot shows that the SIMS = -4.81 + 0.045*GRIP.The scatterplot shows that there's a positive relationship. As the grip gets higher the sims gets higher.

```{r}
# numeric summary
summary.lm(model2)
```
The numeric summary states the SIMS equation and shows that if and when put on a scatterplot it shows as grip goes higher so does sims.




The prediction interval from model1 when arm=94, grip=88 is : 
```{r}
newdata = data.frame(ARM=94, GRIP=88)
predict(model2, newdata, interval= 'prediction')
```

the predicted values is the first value (fit) and the next two values are the lower and upper prediction values.

## third model

```{r}
model3 = lm(SIMS~ARM+GRIP)
model3
```


Model3 shows that SIMS = -5.43 + 0.037*ARM + 0.024*GRIP

```{r}
# numeric summary
summary.lm(model3)
```

The prediction interval from model3 when arm=94, grip=88 is : 
```{r}
newdata = data.frame(ARM=94, GRIP=88)
predict(model3, newdata, interval= 'prediction')
```

the predicted values is the first value (fit) and the next two values are the lower and upper prediction values.

```{r}
anova(model1,model3)
```
This chart compares both model 1 and 3. The null hypothesis has no difference. The alternative hypothesis is that one model is better that the other. The P-Value is 4.994e-06 < 0.05. which means we reject the null hypothesis.Model 3 is the better model because its RSS is smaller.
